Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows

### 2017-03-01 paper.tex
stuff

The input into the workflow is a standard bottom-up tandem-MS dataset obtained from a tryptically digested protein sample along with a corresponding protein sequence database, and the output is a comprehensive set of peptide and PTM identifications.

@@

\subsection{Mass Windows in an Open Search}

>>>>

We first contrast mass-window searches with narrow-mass and open-mass searches, and demonstrate the advantages of using mass-window searches.
The we demonstrate the improvements in the performance of the enhanced G-PTM-D over the original proposed methods, that are due to using mass-window searches.
Finally, we discuss the application of mass-window searches to the discovery of novel modifications.

\subsection{Mass-Window Searches}

\subsubsection{Notch Search vs Narrow-Mass Search}

The purpose of a narrow-mass search is to use the provided precursor mass along with fragmentation spectra information to find an exact match in a protein database.

\subsubsection{Mass Window Searches vs Open-Mass Search}

@@
